Incentives are the biggest barriers to widespread data sharing

### 2021-08-10 new-paper.Rmd
remove sentence: "just archive the data".
Addresses R1-4

Data should be deposited into a relevant domain repository that generates an accession number such as a DOI. For example, gbif for species data, or genbank for genetics data. Information on other domain specific repositories can be found at https://www.nature.com/sdata/policies/repositories. Data not falling into domain repositories can be submitted to research data repositories **zenodo** and **dryad**. In addition to minting DOIs, they also provide citation templates.

@@

Although it is fine to share data among collaborators using temporary cloud storage (like Dropbox, Google Drive), once the paper is public, the data needs to be hosted somewhere persistent. While this approach is useful while iterating on the paper, it does not scale to a larger readership and is highly prone to disappearing (lack of permissions, etc.). Just archive the data. Providing back up data is particularly relevant in light of the case in [@Schleunes2020; @Viglione2020], where data was suspected of being tampered. The use of raw data allowed for issues to be identified, the absence of raw data not being available in other publications created difficulty in verifying the validity of the data.

>>>>

Data should be deposited into a relevant domain repository that generates an accession number such as a DOI. For example, gbif for species data, or genbank for genetics data. A exhaustive searchable list is available at re3data (https://www.re3data.org/) but provides no guidance to researchers. Data that do not fit appropriate domain repositories can be submitted to research data repositories **Zenodo** and **Dryad** which are currently leading the way in best practices for software and data. In addition to minting DOIs, they also provide citation templates.

@@

Although it is fine to share data among collaborators using temporary cloud storage (like Dropbox, Google Drive), once the paper is public, the data needs to be hosted somewhere persistent. While this approach is useful while iterating on the paper, it does not scale to a larger readership and is highly prone to disappearing (lack of permissions, etc.). Providing back up data is particularly relevant in light of the case in [@Schleunes2020; @Viglione2020], where data was suspected of being tampered. The use of raw data allowed for issues to be identified, the absence of raw data not being available in other publications created difficulty in verifying the validity of the data.
